The design flaw of npm and how `everything' broke it

### 2024-02-26 Paper/2/Paper.tex
More work

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column

@@

\begin{abstract}
  npm (Node Package Manager) is a popular package manager owned by GitHub that allows developers
  to share node packages and libraries. This article will review and analyze the design flaw of npm
  and how it was broken by a single package. This article will also review how GitHub responded to
  the incident and what actions they took to prevent it from happening again.
\end{abstract}

\keywords{npm, design flaws, everything, left-pad}

@@

\section{Article Introduction}
Design flaws in software can sometimes lead to security breaches. More often than
not, it is these types of breaches that are the most popularized. However, sometimes
a design flaw can lead to a catastrophic failure that was not even intended
(or initiated) by a bad actor.
With over 1.3 million packages as of April 14th, 2021 \cite{npmblog-stats}, npm is
the world's largest software registry \cite{aboutnpm,w3schools}. As a
result, it has been heavily relied upon by developers for years.

Needless to say, the npm registry is a critical piece of infrastructure for the
entire JavaScript community (and by extension 99\% of websites \cite{w3techs}). Developers
expected that the npm registry would be reliable, secure, and complete. However, the
left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package incident
in 2023 \cite{youtube-everything} have shown that the npm registry is not as reliable
as developers had hoped.

@@

\subsection{The left-pad package}
As a result of Koçulu's deciscion, all of his packages (including left-pad) were removed
from the npm registry. Despite being only 17 lines of code \cite{github-leftpad-code},
millions of packages relied on left-pad \cite{github-leftpad-dependency}. As a result,
many packages that directly or indirectly relied on left-pad broke, including React,
Babel, and Atom.

@@

With the first ever unprecedented un-unpublishing of a package, npm was able to restore
the left-pad package and the packages that relied on it.

@@

With these new policies in place, npm hoped to prevent a similar incident from happening again.
However, these new policies lead towards a new design flaw.

\section{The everything package}
\subsection{Everything's Creation}
In December 2023, a developer by the name PatrickJS decided to work on a package
called `everything'. He teamed up with Evan Boehs, another developer to work on
creating an npm package that would declare every single package in the npm
registry as a dependency. This invovled working around some obscure npm
limitations, such as the maximum number of dependencies being around 800
\cite{youtube-everything}, and the maxiumum package size being 10 MB
\cite{youtube-everything}.

In order to work around these limitations, PatrickJS and Evan Boehs decided to chunk their
dependencies into smaller packages \lstinline|@everything-registry/chunk-0| through to \\
\lstinline|@everything-registry/chunk-4|. At the time there was approximately 2.5 million
packages in the npm registry \cite{youtube-everything}, so sub-chunking was also required.

Unsurprisingly, npm also has a rate limit on how quickly packages can be published. Thus,
PatrickJS and Evan Boehs used a GitHub Action workflow to publish the packages \cite{youtube-everything}.

@@

This was also caused by the fact that the `everything' package depended on a `*' version
of all of its packages, which meant that it matched any version of each of its packages.

\subsection{Historic Related Incidents}
npm was not a stranger to packages and projects before `everything'.

\subsubsection{no-one-left-behind}
was an npm package that was created in 2018 that similarly depended
on 1,000 npm packages \cite{npm-no-one-left-behind-dependencies}. npm managed to remove
the package before it caused significant damage \cite{npm-no-one-left-behind-security}.
It was then re-uploaded under a different name, this time with 33,000 dependencies \cite{socket-everything}.

@@

\subsection{Proposed Solutions}
There have been a few proposed solutions to the design flaw of npm.
It appears that GitHub does not have any immediate plans to change their
policies judging by their response to the `everything' package incident.

@@

\subsubsection{Dependency Analysis}
Another potential solution is to analyze the dependencies of a package before
allowing it to be published. If a package depends on every other package in the
registry, it could be flagged for review by the npm team.

@@

@@

>>>>

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with 
% conference information in first column

@@

\begin{abstract}
  npm (Node Package Manager) is a popular package manager owned by GitHub that
  allows developers to share node packages and libraries. This article will
  review and analyze the design flaw of npm and how it was broken by a single
  package, and will also review how GitHub responded to the incident and what
  actions they took in response.
\end{abstract}

\keywords{npm, github, design flaws, everything, left-pad}

@@

\section{Article Introduction}
Design flaws in software can sometimes lead to security breaches. More often
than not, it is these types of design flaws that are the most popularized.
However, sometimes a design flaw can lead to a catastrophic failure that was not
even intended (or initiated) by a bad actor. With over 1.3 million packages as
of April 14th, 2021 \cite{npmblog-stats}, npm is the world's largest software
registry \cite{aboutnpm,w3schools}. As a result, it has been heavily relied upon
by developers for years.

The npm registry is a critical piece of infrastructure for the entire JavaScript
community (and by extension, 99\% of websites \cite{w3techs}). Developers expect
that the npm registry would be reliable, secure, and complete. However, the
left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
incident in 2023 \cite{youtube-everything} have shown that the npm registry is
not as reliable as developers had hoped.

@@

\subsection{The left-pad package}
As a result of Koçulu's deciscion, all of his packages (including left-pad) were
removed from the npm registry. Despite being only 17 lines of code
\cite{github-leftpad-code}, millions of packages relied on left-pad
\cite{github-leftpad-dependency}. As a result, many packages that directly or
indirectly relied on left-pad broke, including React, Babel, and Atom
\cite{npmblog-leftpad}.

@@

With the first ever unprecedented un-unpublishing of a package, npm was able to
restore the left-pad package and the packages that relied on it
\cite{npmblog-leftpad}.

@@

With these new policies in place, npm hoped to prevent a similar incident from
happening again. However, these new policies lead towards a new unforseen design
flaw.

\section{The everything package}
\subsection{Everything's Creation}
In December 2023, a developer by the name PatrickJS decided to work on a package
called `everything'. He teamed up with Evan Boehs and a few other developers to
work on creating an npm package that would declare every package in the npm
registry as a dependency \cite{uncenter-blog-everything}. This invovled working
around obscure npm limitations, such as the maximum number of dependencies being
around 800 \cite{uncenter-blog-everything, youtube-everything}, and the maxiumum
package size being 10 MB \cite{uncenter-blog-everything, youtube-everything}.

In order to work around these limitations, PatrickJS and Evan Boehs decided to
chunk their dependencies into smaller packages
\lstinline|@everything-registry/chunk-0| through to \\
\lstinline|@everything-registry/chunk-4|. At the time there was approximately
2.5 million packages in the npm registry \cite{youtube-everything}, so
sub-chunking was also required \cite{youtube-everything}.

Unsurprisingly, npm also has a rate limit on how quickly packages can be
published \cite{npm-ratelimiting}. Thus, PatrickJS and Evan Boehs used a GitHub
Action workflow to publish the packages
\cite{youtube-everything,uncenter-blog-everything}.

@@

This was also caused by the fact that the `everything' package depended on a `*'
version of all of its packages, which meant that it matched any version of each
of its packages. Even if developers published a new version of their packages,
the `everything' package would actually just depend on both the old and new
versions of the package \cite{uncenter-blog-everything}.

\subsection{Historic Related Incidents}
npm was no a stranger to packages and projects similar to `everything'.

\subsubsection{no-one-left-behind}
was an npm package that was created in 2018 that depended on 1,000 npm packages
\cite{npm-no-one-left-behind-dependencies}. npm managed to remove the package
before it caused significant damage \cite{npm-no-one-left-behind-security}. It
was then re-uploaded under a different name, this time with 33,000 dependencies
\cite{socket-everything}.

@@

\subsection{Proposed Solutions}
There have been a few proposed solutions to the design flaw of npm. It appears
that GitHub does not have any immediate plans to change their policies judging
by their response to the `everything' package incident
\cite{uncenter-blog-everything}.

@@

Realistically, an initial package should not depend on more than a few hundred
other packages (especially not directly). This would be a good indicator that
the package is not well-designed, and would allow the npm team to review the
package before allowing it to be published.

The idea of rate-limiting the growth of a package's dependencies would require
careful consideration and implementation, as it could potentially break existing
packages that rely on a large number of dependencies.

\subsubsection{Dependency Analysis}
Another potential solution is to analyze the dependencies of a package before
allowing it to be published. If a package depends on every other package in the
registry (or a significant portion of it), it could be flagged for review by the
npm team.

Static code analysis could additionally be used to detect dependencies that are
not actually used by the package, and flag the package for review.

@@

While there may not be a perfect policy that works for every package, npm could
consider implementing a review process for new packages that are published to
the registry from new developer (accounts), or from developers that have not
published a package in a long time.

@@

Such a review process would require some form of automation and user reporting
system. Considering npm is free to use \cite{npm-tos}, it may not be feasible to
have sufficient staffing for this process.

\subsubsection{Accept the Flaw}
The route that GitHub seems to take (for now at least) is to accept the flaw and
mark packages like `everything' as against their terms of service
\cite{uncenter-blog-everything}. While this may have worked in the case of the
`everything' package, it is not a long-term solution to the problem. GitHub will
most likely have to automate some form of detection and removal of packages like
`everything' in the future.
